\papertitle

### 2021-05-31 source_separation/paper/paper.tex
Add details on OpenUnmix's standardization

			\subsubsection{Music source separation}
			\textbf{Open-Unmix}~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich2017}. It is actually composed of multiple models that are trained for each instrumental target. Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectional LSTM network. Open-Unmix operates on the Short Time Fourier Transform (STFT) of the input mixture, which is first standardized. It predicts the target by multiplying the output of the LSTM network with the magnitude spectrogram of the input, essentially applying a mask. Open-Unmix also uses Wiener filtering as a last processing step.

>>>>

			\subsubsection{Music source separation}
			\textbf{Open-Unmix}~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich2017}. It is actually composed of multiple models that are trained for each instrumental target. Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectional LSTM network. Open-Unmix operates on the Short Time Fourier Transform (STFT) of the input mixture, which is first standardized using the global mean and standard deviation for every frequency bin across all frames. It predicts the target by multiplying the output of the LSTM network with the magnitude spectrogram of the input, essentially applying a mask. Open-Unmix also uses Wiener filtering as a last processing step.
